---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%")
  
library(dplyr)
library(leaflet)
library(PakIndicatorsApp)

```

# PakIndicatorsApp

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

The goal of PakIndicatorsApp is to provide a scaffolding for the schematic and efficient management and visualization of the district level indicators of Pakistan, for multiple rounds of the household surveys. It covers a variety of socio-economic (SDG related) indicators ranging from  poverty incidence, labor market outcomes, health and nutrition, stunting and wasting, food security and so on.
We will be updating the app based on the data availability and revisions/feedback.

##Data Coverage

Currently, the portal covers HIES, PLSM, MICS and NNS surveys. (various rounds from 2004 to 2020)


##Usage

The app can specifically be used to explore spatial disparities in development outcomes at district (adm2) level in the country.

## Installation

You can install the development version of PakIndicatorsApp like so:

``` r
# To install the application 
remotes::install_github("szhaider/PakIndicatorsApp")
```

## Example

This is a basic details about the data used in the application:

```{r Doamins, echo=FALSE}
## Doamins covered
unique(Pak_Indicators_Data$domain)

```


```{r time, echo=FALSE}
##Years Covered
unique(Pak_Indicators_Data$year)

```

```{r surveys, echo=FALSE}
##Surveys over the years
unique(Pak_Indicators_Data$year_1)

```


